---
title: "The Map of Gender Inequality Index"  
---

## Introduction

```{r message=FALSE, warning=FALSE, include=FALSE}
```

The **Gender Inequality Index (GII)** is a composite measure developed by the United Nations Development Programme (UNDP) to assess gender disparities in various dimensions of human development[^1]. It highlights the inequalities between men and women in three critical areas: reproductive health, empowerment, and labor market participation.

[^1]: [1]United Nations Development Programme (2023) *Gender Inequality Index (GII) - Statistical Annex 2023/2024.* <https://hdr.undp.org/sites/default/files/2023-24_HDR/HDR23-24_Statistical_Annex_GII_Table.xlsx>

This page transforms those statistical insights into an interactive map, allowing users to explore gender inequality patterns geographically.The map of the world provided by ESRI[^2].

[^2]: [2]ArcGIS Hub (n.d.) *World Countries Generalized.* <https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-0.207545%2C0.000000%2C1.41>

```{r message=FALSE, warning=FALSE, include=FALSE}

library(sf)
library(here)
library(dplyr)
library(countrycode)
library(readr)
library(janitor)

World_map<-st_read(here::here("World_Countries_(Generalized)_9029012925078512962.geojson"))
Index2 <- read_csv(here::here("inequality indexUTF8.csv"))

World_map2<-World_map %>%
  mutate(isoname=countrycode::countrycode(World_map[[2]], origin="country.name", destination = 'iso.name.en') )
Index_renamed<-Index2 %>%
  mutate(isoname=countrycode::countrycode(Index2[[2]], origin="country.name", destination = 'iso.name.en') )

World_Index<-World_map2 %>%
  left_join(Index_renamed, by = "isoname") %>%
  clean_names() %>%
  distinct() 
```

```{r map drawing, echo=FALSE, message=FALSE, warning=FALSE}


tmap_mode("view")
tm_shape(World_Index) +
  tm_polygons("gender_inequality_index", 
               alpha = 0.8, 
               title = "Gender Inequality Index",
               style = "cont", 
               palette = "Blues", 
               border.col = "black", popup.vars = "gender_inequality_index") +
  tm_borders() +
  tm_layout(legend.outside = TRUE) 

```

## Referance
